# Data Analysis 

## Sector Weights
First, sector weights were calculated over time for both EUSA and USMV. Plots were made by sector and displayed to compare the relative weights of EUSA and USMV. 

*Sector Weight Summary Statistics:*

```{r}
data(usa_percent)
data(minvol_percent)

## Summary statistics of EUSA sector weights
head(usa_percent)
tail(usa_percent)
summary(usa_percent)

## Summary statistics of USMV sector weights
head(minvol_percent)
tail(minvol_percent)
summary(minvol_percent)
```

*Sector Weights for EUSA and USMV:*

```{r, echo = FALSE}
## Energy
Eng1 <- usa_percent[which(usa_percent$sector_name=="Energy"), ]
Eng2 <- minvol_percent[which(minvol_percent$sector_name=="Energy"), ]
ggplot(Eng1, aes(date, percent, colour = "USA")) + geom_line() +  
ggtitle("EUSA and USMV Energy Sector Weights") + xlab("Time") + ylab("Sector Weight") +
geom_line(data = Eng2, aes(x=date, y=percent, colour="Min Vol"),show.legend = TRUE)

## Finacials
Fin1 <- usa_percent[which(usa_percent$sector_name=="Financials"), ]
Fin2 <- minvol_percent[which(minvol_percent$sector_name=="Financials"), ]
ggplot(Fin1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Financial Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + 
geom_line(data = Fin2, aes(x=date, y=percent, colour="Min Vol"),show.legend = TRUE)

## Consumer Staples
ConStap1 <- usa_percent[which(usa_percent$sector_name=="Consumer Staples"), ]
ConStap2 <- minvol_percent[which(minvol_percent$sector_name=="Consumer Staples"), ]
ggplot(ConStap1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Consumer Staples Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = ConStap2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Consumer Discretionary
ConDis1 <- usa_percent[which(usa_percent$sector_name=="Consumer Discretionary"), ]
ConDis2 <- minvol_percent[which(minvol_percent$sector_name=="Consumer Discretionary"), ]
ggplot(ConDis1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Consumer Discretionary Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = ConDis2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Health Care
Health1 <- usa_percent[which(usa_percent$sector_name=="Health Care"), ]
Health2 <- minvol_percent[which(minvol_percent$sector_name=="Health Care"), ]
ggplot(Health1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Health Care Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Health2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Industrials
Ind1 <- usa_percent[which(usa_percent$sector_name=="Industrials"), ]
Ind2 <- minvol_percent[which(minvol_percent$sector_name=="Industrials"), ]
ggplot(Ind1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Industrials Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Ind2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Information Technology
IT1 <- usa_percent[which(usa_percent$sector_name=="Information Technology"), ]
IT2 <- minvol_percent[which(minvol_percent$sector_name=="Information Technology"), ]
ggplot(IT1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Information Technology Sector Weights") + 
xlab("Time") + ylab("Sector Weight") + geom_line(data = IT2, aes(x=date, y=percent,
colour="Min Vol"),show.legend = TRUE)

## Materials
Mat1 <- usa_percent[which(usa_percent$sector_name=="Materials"), ]
Mat2 <- minvol_percent[which(minvol_percent$sector_name=="Materials"), ]
ggplot(Mat1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Materials Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Mat2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Utilites
Util1 <- usa_percent[which(usa_percent$sector_name=="Utilities"), ]
Util2 <- minvol_percent[which(minvol_percent$sector_name=="Utilities"), ]
ggplot(Util1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Utilities Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Util2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Telecommunication Services
Telecom1 <- usa_percent[which(usa_percent$sector_name=="Telecommunications"), ]
Telecom2 <- minvol_percent[which(minvol_percent$sector_name=="Telecommunications"), ]
ggplot(Telecom1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("EUSA and USMV Telecommunications Sector Weights") + 
xlab("Time") + ylab("Sector Weight") + geom_line(data = Telecom2, aes(x=date, 
y=percent, colour="Min Vol"),show.legend = TRUE)
```

## USMV Constituent Trailing Volatilities 
Data was collected from a year before the creation of the USMV index. The data was collected from 10/04/2010 to 12/30/2016, was collected from WRDS for the 300 historical constituents of the MSCI Minimum Volatility Index (USMV), to find their 252-day (annual) trailing volatility. 

```{r, echo = FALSE}
library(ggplot2)
library(mscidata)

#AAP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AAP, aes(Date, SD)) + ggtitle("AAP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ABBV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ABBV, aes(Date, SD)) + ggtitle("ABBV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ABC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ABC, aes(Date, SD)) + ggtitle("ABC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ABT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ABT, aes(Date, SD)) + ggtitle("ABT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ACE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ACE, aes(Date, SD)) + ggtitle("ACE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ACGL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ACGL, aes(Date, SD)) + ggtitle("ACGL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ACN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ACN, aes(Date, SD)) + ggtitle("ACN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ADBE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ADBE, aes(Date, SD)) + ggtitle("ADBE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ADP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ADP, aes(Date, SD)) + ggtitle("ADP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AEP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AEP, aes(Date, SD)) + ggtitle("AEP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AET 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AET, aes(Date, SD)) + ggtitle("AET 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AGN, aes(Date, SD)) + ggtitle("AGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AGNC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AGNC, aes(Date, SD)) + ggtitle("AGNC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ALL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ALL, aes(Date, SD)) + ggtitle("ALL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ALTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ALTR, aes(Date, SD)) + ggtitle("ALTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AMGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AMGN, aes(Date, SD)) + ggtitle("AMGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AMT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AMT, aes(Date, SD)) + ggtitle("AMT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ANSS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ANSS, aes(Date, SD)) + ggtitle("ANSS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ANTM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ANTM, aes(Date, SD)) + ggtitle("ANTM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AON 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AON, aes(Date, SD)) + ggtitle("AON 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#APH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(APH, aes(Date, SD)) + ggtitle("APH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AR, aes(Date, SD)) + ggtitle("AR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ARMK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ARMK, aes(Date, SD)) + ggtitle("ARMK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ATVI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ATVI, aes(Date, SD)) + ggtitle("ATVI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AVB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AVB, aes(Date, SD)) + ggtitle("AVB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AWK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AWK, aes(Date, SD)) + ggtitle("AWK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AXS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AXS, aes(Date, SD)) + ggtitle("AXS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AZO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AZO, aes(Date, SD)) + ggtitle("AZO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BAX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BAX, aes(Date, SD)) + ggtitle("BAX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BBBY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BBBY, aes(Date, SD)) + ggtitle("BBBY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BCR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BCR, aes(Date, SD)) + ggtitle("BCR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BDX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BDX, aes(Date, SD)) + ggtitle("BDX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BIIB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BIIB, aes(Date, SD)) + ggtitle("BIIB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BMC, aes(Date, SD)) + ggtitle("BMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BMY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BMY, aes(Date, SD)) + ggtitle("BMY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BR, aes(Date, SD)) + ggtitle("BR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BRX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BRX, aes(Date, SD)) + ggtitle("BRX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BSX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BSX, aes(Date, SD)) + ggtitle("BSX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BXLT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BXLT, aes(Date, SD)) + ggtitle("BXLT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BXP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BXP, aes(Date, SD)) + ggtitle("BXP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CA, aes(Date, SD)) + ggtitle("CA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CAG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CAG, aes(Date, SD)) + ggtitle("CAG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CAH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CAH, aes(Date, SD)) + ggtitle("CAH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CB, aes(Date, SD)) + ggtitle("CB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CCI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CCI, aes(Date, SD)) + ggtitle("CCI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CDNS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CDNS, aes(Date, SD)) + ggtitle("CDNS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CELG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CELG, aes(Date, SD)) + ggtitle("CELG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CHD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CHD, aes(Date, SD)) + ggtitle("CHD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CHRW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CHRW, aes(Date, SD)) + ggtitle("CHRW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CHTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CHTR, aes(Date, SD)) + ggtitle("CHTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CI, aes(Date, SD)) + ggtitle("CI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CINF 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CINF, aes(Date, SD)) + ggtitle("CINF 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CL, aes(Date, SD)) + ggtitle("CL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CLX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CLX, aes(Date, SD)) + ggtitle("CLX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CMCSA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CMCSA, aes(Date, SD)) + ggtitle("CMCSA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CMCSK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CMCSK, aes(Date, SD)) + ggtitle("CMCSK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CME 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CME, aes(Date, SD)) + ggtitle("CME 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CMG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CMG, aes(Date, SD)) + ggtitle("CMG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COG, aes(Date, SD)) + ggtitle("COG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COLE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COLE, aes(Date, SD)) + ggtitle("COLE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COO, aes(Date, SD)) + ggtitle("COO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COP, aes(Date, SD)) + ggtitle("COP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COST 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COST, aes(Date, SD)) + ggtitle("COST 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COV, aes(Date, SD)) + ggtitle("COV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CPB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CPB, aes(Date, SD)) + ggtitle("CPB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CPT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CPT, aes(Date, SD)) + ggtitle("CPT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CRC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CRC, aes(Date, SD)) + ggtitle("CRC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CSCO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CSCO, aes(Date, SD)) + ggtitle("CSCO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CTAS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CTAS, aes(Date, SD)) + ggtitle("CTAS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CTL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CTL, aes(Date, SD)) + ggtitle("CTL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CVS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CVS, aes(Date, SD)) + ggtitle("CVS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CVX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CVX, aes(Date, SD)) + ggtitle("CVX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#D 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(D, aes(Date, SD)) + ggtitle("D 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DD, aes(Date, SD)) + ggtitle("DD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DE, aes(Date, SD)) + ggtitle("DE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DG, aes(Date, SD)) + ggtitle("DG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DGX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DGX, aes(Date, SD)) + ggtitle("DGX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DHR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DHR, aes(Date, SD)) + ggtitle("DHR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DIS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DIS, aes(Date, SD)) + ggtitle("DIS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DLR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DLR, aes(Date, SD)) + ggtitle("DLR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DLTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DLTR, aes(Date, SD)) + ggtitle("DLTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DNB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DNB, aes(Date, SD)) + ggtitle("DNB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DPS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DPS, aes(Date, SD)) + ggtitle("DPS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DRI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DRI, aes(Date, SD)) + ggtitle("DRI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DTV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DTV, aes(Date, SD)) + ggtitle("DTV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DUK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DUK, aes(Date, SD)) + ggtitle("DUK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DVA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DVA, aes(Date, SD)) + ggtitle("DVA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EBAY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EBAY, aes(Date, SD)) + ggtitle("EBAY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ECL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ECL, aes(Date, SD)) + ggtitle("ECL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ED 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ED, aes(Date, SD)) + ggtitle("ED 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EFX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EFX, aes(Date, SD)) + ggtitle("EFX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EGN, aes(Date, SD)) + ggtitle("EGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EMC, aes(Date, SD)) + ggtitle("EMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EQR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EQR, aes(Date, SD)) + ggtitle("EQR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ES 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ES, aes(Date, SD)) + ggtitle("ES 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ESRX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ESRX, aes(Date, SD)) + ggtitle("ESRX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ESS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ESS, aes(Date, SD)) + ggtitle("ESS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EW, aes(Date, SD)) + ggtitle("EW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EXPD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EXPD, aes(Date, SD)) + ggtitle("EXPD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EXR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EXR, aes(Date, SD)) + ggtitle("EXR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FB, aes(Date, SD)) + ggtitle("FB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FDO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FDO, aes(Date, SD)) + ggtitle("FDO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FIS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FIS, aes(Date, SD)) + ggtitle("FIS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FISV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FISV, aes(Date, SD)) + ggtitle("FISV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FL, aes(Date, SD)) + ggtitle("FL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FNF 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FNF, aes(Date, SD)) + ggtitle("FNF 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FRC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FRC, aes(Date, SD)) + ggtitle("FRC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FRT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FRT, aes(Date, SD)) + ggtitle("FRT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FRX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FRX, aes(Date, SD)) + ggtitle("FRX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FTR, aes(Date, SD)) + ggtitle("FTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FTV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FTV, aes(Date, SD)) + ggtitle("FTV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GAS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GAS, aes(Date, SD)) + ggtitle("GAS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GD, aes(Date, SD)) + ggtitle("GD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GGP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GGP, aes(Date, SD)) + ggtitle("GGP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GILD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GILD, aes(Date, SD)) + ggtitle("GILD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GIS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GIS, aes(Date, SD)) + ggtitle("GIS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GOOG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GOOG, aes(Date, SD)) + ggtitle("GOOG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GOOGL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GOOGL, aes(Date, SD)) + ggtitle("GOOGL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GPC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GPC, aes(Date, SD)) + ggtitle("GPC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GR, aes(Date, SD)) + ggtitle("GR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GWW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GWW, aes(Date, SD)) + ggtitle("GWW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HCN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HCN, aes(Date, SD)) + ggtitle("HCN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HCP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HCP, aes(Date, SD)) + ggtitle("HCP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HD, aes(Date, SD)) + ggtitle("HD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HNZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HNZ, aes(Date, SD)) + ggtitle("HNZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HOLX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HOLX, aes(Date, SD)) + ggtitle("HOLX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HRL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HRL, aes(Date, SD)) + ggtitle("HRL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HSIC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HSIC, aes(Date, SD)) + ggtitle("HSIC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HSY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HSY, aes(Date, SD)) + ggtitle("HSY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HUM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HUM, aes(Date, SD)) + ggtitle("HUM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#IBM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(IBM, aes(Date, SD)) + ggtitle("IBM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#IHS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(IHS, aes(Date, SD)) + ggtitle("IHS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#INCO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(INCO, aes(Date, SD)) + ggtitle("INCO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#INTC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(INTC, aes(Date, SD)) + ggtitle("INTC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#INTU 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(INTU, aes(Date, SD)) + ggtitle("INTU 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ISRG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ISRG, aes(Date, SD)) + ggtitle("ISRG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#IT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(IT, aes(Date, SD)) + ggtitle("IT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#JBHT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(JBHT, aes(Date, SD)) + ggtitle("JBHT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#JNJ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(JNJ, aes(Date, SD)) + ggtitle("JNJ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#JWN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(JWN, aes(Date, SD)) + ggtitle("JWN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#K 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(K, aes(Date, SD)) + ggtitle("K 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KFT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KFT, aes(Date, SD)) + ggtitle("KFT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KMB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KMB, aes(Date, SD)) + ggtitle("KMB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KMI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KMI, aes(Date, SD)) + ggtitle("KMI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KMR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KMR, aes(Date, SD)) + ggtitle("KMR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KO, aes(Date, SD)) + ggtitle("KO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KRFT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KRFT, aes(Date, SD)) + ggtitle("KRFT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LB, aes(Date, SD)) + ggtitle("LB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LDOS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LDOS, aes(Date, SD)) + ggtitle("LDOS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LH, aes(Date, SD)) + ggtitle("LH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LIFE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LIFE, aes(Date, SD)) + ggtitle("LIFE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LLTC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LLTC, aes(Date, SD)) + ggtitle("LLTC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LLY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LLY, aes(Date, SD)) + ggtitle("LLY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LMT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LMT, aes(Date, SD)) + ggtitle("LMT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LO, aes(Date, SD)) + ggtitle("LO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LOW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LOW, aes(Date, SD)) + ggtitle("LOW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LUV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LUV, aes(Date, SD)) + ggtitle("LUV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MA, aes(Date, SD)) + ggtitle("MA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MAC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MAC, aes(Date, SD)) + ggtitle("MAC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MAT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MAT, aes(Date, SD)) + ggtitle("MAT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MCD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MCD, aes(Date, SD)) + ggtitle("MCD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MCK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MCK, aes(Date, SD)) + ggtitle("MCK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MDLZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MDLZ, aes(Date, SD)) + ggtitle("MDLZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MDT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MDT, aes(Date, SD)) + ggtitle("MDT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MHFI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MHFI, aes(Date, SD)) + ggtitle("MHFI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MKC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MKC, aes(Date, SD)) + ggtitle("MKC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MKL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MKL, aes(Date, SD)) + ggtitle("MKL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MMC, aes(Date, SD)) + ggtitle("MMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MMM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MMM, aes(Date, SD)) + ggtitle("MMM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MNK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MNK, aes(Date, SD)) + ggtitle("MNK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MO, aes(Date, SD)) + ggtitle("MO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MON 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MON, aes(Date, SD)) + ggtitle("MON 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MRK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MRK, aes(Date, SD)) + ggtitle("MRK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MSFT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MSFT, aes(Date, SD)) + ggtitle("MSFT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MSI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MSI, aes(Date, SD)) + ggtitle("MSI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MTB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MTB, aes(Date, SD)) + ggtitle("MTB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NEE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NEE, aes(Date, SD)) + ggtitle("NEE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NEM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NEM, aes(Date, SD)) + ggtitle("NEM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NKE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NKE, aes(Date, SD)) + ggtitle("NKE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NLSN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NLSN, aes(Date, SD)) + ggtitle("NLSN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NLY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NLY, aes(Date, SD)) + ggtitle("NLY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NNN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NNN, aes(Date, SD)) + ggtitle("NNN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NOC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NOC, aes(Date, SD)) + ggtitle("NOC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NST 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NST, aes(Date, SD)) + ggtitle("NST 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NWSA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NWSA, aes(Date, SD)) + ggtitle("NWSA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#O 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(O, aes(Date, SD)) + ggtitle("O 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#OCR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(OCR, aes(Date, SD)) + ggtitle("OCR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#OMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(OMC, aes(Date, SD)) + ggtitle("OMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ORCL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ORCL, aes(Date, SD)) + ggtitle("ORCL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ORLY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ORLY, aes(Date, SD)) + ggtitle("ORLY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#OXY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(OXY, aes(Date, SD)) + ggtitle("OXY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PAYX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PAYX, aes(Date, SD)) + ggtitle("PAYX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PBCT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PBCT, aes(Date, SD)) + ggtitle("PBCT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PCG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PCG, aes(Date, SD)) + ggtitle("PCG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PCP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PCP, aes(Date, SD)) + ggtitle("PCP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PDCO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PDCO, aes(Date, SD)) + ggtitle("PDCO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PEP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PEP, aes(Date, SD)) + ggtitle("PEP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PETM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PETM, aes(Date, SD)) + ggtitle("PETM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PFE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PFE, aes(Date, SD)) + ggtitle("PFE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PG, aes(Date, SD)) + ggtitle("PG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PGN, aes(Date, SD)) + ggtitle("PGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PGR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PGR, aes(Date, SD)) + ggtitle("PGR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PM, aes(Date, SD)) + ggtitle("PM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#POM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(POM, aes(Date, SD)) + ggtitle("POM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PRE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PRE, aes(Date, SD)) + ggtitle("PRE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PRGO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PRGO, aes(Date, SD)) + ggtitle("PRGO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PSA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PSA, aes(Date, SD)) + ggtitle("PSA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PSX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PSX, aes(Date, SD)) + ggtitle("PSX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PX, aes(Date, SD)) + ggtitle("PX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PYPL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PYPL, aes(Date, SD)) + ggtitle("PYPL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#Q 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(Q, aes(Date, SD)) + ggtitle("Q 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#QCOM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(QCOM, aes(Date, SD)) + ggtitle("QCOM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RAI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RAI, aes(Date, SD)) + ggtitle("RAI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RE, aes(Date, SD)) + ggtitle("RE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#REG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(REG, aes(Date, SD)) + ggtitle("REG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RMD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RMD, aes(Date, SD)) + ggtitle("RMD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RNR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RNR, aes(Date, SD)) + ggtitle("RNR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ROST 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ROST, aes(Date, SD)) + ggtitle("ROST 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RSG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RSG, aes(Date, SD)) + ggtitle("RSG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RTN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RTN, aes(Date, SD)) + ggtitle("RTN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SBAC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SBAC, aes(Date, SD)) + ggtitle("SBAC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SBUX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SBUX, aes(Date, SD)) + ggtitle("SBUX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SE, aes(Date, SD)) + ggtitle("SE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SHW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SHW, aes(Date, SD)) + ggtitle("SHW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SIAL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SIAL, aes(Date, SD)) + ggtitle("SIAL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SJM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SJM, aes(Date, SD)) + ggtitle("SJM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SLB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SLB, aes(Date, SD)) + ggtitle("SLB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SNI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SNI, aes(Date, SD)) + ggtitle("SNI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SNPS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SNPS, aes(Date, SD)) + ggtitle("SNPS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SO, aes(Date, SD)) + ggtitle("SO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SPG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SPG, aes(Date, SD)) + ggtitle("SPG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SRCL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SRCL, aes(Date, SD)) + ggtitle("SRCL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SRE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SRE, aes(Date, SD)) + ggtitle("SRE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#STJ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(STJ, aes(Date, SD)) + ggtitle("STJ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#STZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(STZ, aes(Date, SD)) + ggtitle("STZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SYK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SYK, aes(Date, SD)) + ggtitle("SYK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SYMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SYMC, aes(Date, SD)) + ggtitle("SYMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SYY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SYY, aes(Date, SD)) + ggtitle("SYY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#T 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(T, aes(Date, SD)) + ggtitle("T 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TGT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TGT, aes(Date, SD)) + ggtitle("TGT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TJX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TJX, aes(Date, SD)) + ggtitle("TJX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TMO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TMO, aes(Date, SD)) + ggtitle("TMO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TRV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TRV, aes(Date, SD)) + ggtitle("TRV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TSS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TSS, aes(Date, SD)) + ggtitle("TSS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TXN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TXN, aes(Date, SD)) + ggtitle("TXN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UDR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UDR, aes(Date, SD)) + ggtitle("UDR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UHS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UHS, aes(Date, SD)) + ggtitle("UHS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ULTA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ULTA, aes(Date, SD)) + ggtitle("ULTA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UNH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UNH, aes(Date, SD)) + ggtitle("UNH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UNP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UNP, aes(Date, SD)) + ggtitle("UNP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UPS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UPS, aes(Date, SD)) + ggtitle("UPS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#USB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(USB, aes(Date, SD)) + ggtitle("USB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#USD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(USD, aes(Date, SD)) + ggtitle("USD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UTX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UTX, aes(Date, SD)) + ggtitle("UTX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#V 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(V, aes(Date, SD)) + ggtitle("V 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VAL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VAL, aes(Date, SD)) + ggtitle("VAL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VAR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VAR, aes(Date, SD)) + ggtitle("VAR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VFC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VFC, aes(Date, SD)) + ggtitle("VFC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VMW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VMW, aes(Date, SD)) + ggtitle("VMW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VNO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VNO, aes(Date, SD)) + ggtitle("VNO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VNTV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VNTV, aes(Date, SD)) + ggtitle("VNTV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VRSK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VRSK, aes(Date, SD)) + ggtitle("VRSK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VRSN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VRSN, aes(Date, SD)) + ggtitle("VRSN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VTR, aes(Date, SD)) + ggtitle("VTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VZ, aes(Date, SD)) + ggtitle("VZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WAT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WAT, aes(Date, SD)) + ggtitle("WAT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WCN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WCN, aes(Date, SD)) + ggtitle("WCN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WEC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WEC, aes(Date, SD)) + ggtitle("WEC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WFC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WFC, aes(Date, SD)) + ggtitle("WFC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WIN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WIN, aes(Date, SD)) + ggtitle("WIN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WM, aes(Date, SD)) + ggtitle("WM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WMT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WMT, aes(Date, SD)) + ggtitle("WMT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WPI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WPI, aes(Date, SD)) + ggtitle("WPI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WR, aes(Date, SD)) + ggtitle("WR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WRB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WRB, aes(Date, SD)) + ggtitle("WRB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WSH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WSH, aes(Date, SD)) + ggtitle("WSH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#XEL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(XEL, aes(Date, SD)) + ggtitle("XEL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#XOM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(XOM, aes(Date, SD)) + ggtitle("XOM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#Y 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(Y, aes(Date, SD)) + ggtitle("Y 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#YHOO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(YHOO, aes(Date, SD)) + ggtitle("YHOO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#YUM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(YUM, aes(Date, SD)) + ggtitle("YUM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ZAYO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ZAYO, aes(Date, SD)) + ggtitle("ZAYO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ZBH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ZBH, aes(Date, SD)) + ggtitle("ZBH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ZTS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ZTS, aes(Date, SD)) + ggtitle("ZTS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")
```

