---
title: "05 - Model"
author: "John Gilheany"
date: "9/13/2017"
output: html_document
---

# Model 
Once the final data set was created and cleaned, with a number of response variables including trailing beta, trailing vol, and price to book value, and an associated outcome. The outcome measured whether or not a stock was in the Min Vol index or not (1 if in, 0 if not in).

A snippet of the final data set is shown below
```{r}
data(monthly_test1)
head(monthly_test1)

tail(monthly_test1)

summary(monthly_test1)
```

Given the data, a logit regression was run on the entire pool of data. Looking at all of the historical data and stock various characteristics, this would model the log odds of a stock being in the minimum volatility index as a combination of the linear predictors mentioned. Several models will be run in a panel, including one by month, and one by the entire pool of data.

## Model 1: Entire Data Set
The first logit model that will be run is for the entire pool of data. 
```{r}
# Model 1
logit1 <- glm(binary ~  beta + volatility + price_to_book, data = monthly_test1, family = "binomial")

# Summary of Model 1
summary(logit1)

# Coefficient Interpretation
exp(coef(logit1))

# Confidence interval of variavle
confint.default(logit1)
``` 

## Model 2: Monthly

## Model 3: Panel Regression
