--- 
title: "Thesis"
author: "John Gilheany"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::pdf_book
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Thesis stuff"
---

# Opening Comments

<!--chapter:end:index.Rmd-->


# Introduction {#intro}

<!--chapter:end:01-intro.Rmd-->


# Literature Review
## High Returns from Low Risk By Pim van Vliet and Jan De Koning
## Betting Against Correlation: Testing Theories of the Low-Risk Effect
## Price Response to Factor Index Additions and Deletions 
## Benchmarks as Limits to Arbitrage: Understanding the Low-Volatility Anomaly
## Betting Against Beta
## The Low-Risk Anomaly: A Decomposition into Micro and Macro Effects

<!--chapter:end:02-literature.Rmd-->


# Data Collection and Summary Statistics
## EUSA and USMV Data Compilation
## EUSA and USMV Data Cleaning
### Non-US Exchanges
### Unrecognized Tickers
### Price Discrepancies
## EUSA and USMV Data Overview 
## EUSA and USMV Data Check
### Weights
### Comparing actual ETF returns to constructed ETF returns for EUSA and USMV
### Change in 5 largest holdings by average weight for EUSA and USMV

<!--chapter:end:03-data_collection.Rmd-->


# Data Analysis 
## Sector Weights
## Summary statistics of EUSA sector weights
## Summary statistics of USMV sector weights
## Energy
## Finacials
## Consumer Staples
## Consumer Discretionary
## Health Care
## Industrials
## Information Technology
## Materials
## Utilites
## Telecommunication Services
## EUSA Constituent Trailing Volatilities 
## EUSA Constituent Trailing Betas 
## EUSA Constituent Price to Book Ratios 

<!--chapter:end:04-data_analysis.Rmd-->

---
title: "05 - Model"
author: "John Gilheany"
date: "9/13/2017"
output:
  pdf_document: default
  html_document: default
---

# Model 
Once the final data set was created and cleaned, with a number of response variables including trailing beta, trailing vol, and price to book value, and an associated outcome. The outcome measured whether or not a stock was in the Min Vol index or not (1 if in, 0 if not in).

A snippet of the final data set is shown below
```{r}
data(monthly_final)
head(monthly_final)

tail(monthly_final)

summary(monthly_final)
```

Given the data, a logit regression was run on the entire pool of data. Looking at all of the historical data and stock various characteristics, this would model the log odds of a stock being in the minimum volatility index as a combination of the linear predictors mentioned. Several models will be run in a panel, including one by month, and one by the entire pool of data.

## Model 1: Entire Data Set (Monthly)
The first logit model that will be run is for the entire pool of data. 
```{r}
# Model 1
logit1 <- glm(index_now ~  volatility + beta + price_to_book + index_before, data = monthly_final, family = "binomial")
# Summary of Model 1
summary(logit1)

# Coefficient Interpretation
exp(coef(logit1))

# Confidence interval of variable
confint.default(logit1)
``` 

Looking at the monthly data is not a true representation of the results, because the index is rebalanced once every six months - not once a month. 




## Model 2: Monthly

## Model 3: Panel Regression

<!--chapter:end:05-Model.Rmd-->


# Conclusion  
## Model 1: Entire Data Set 
## Model 2: Monthly
## Model 3: Panel Regression

<!--chapter:end:06-Conclusion.Rmd-->


# Bibliography 

<!--chapter:end:08-bibliography.Rmd-->

