---
title: "Vignette"
author: "John Gilheany"
date: "2/26/2017"
output: pdf_document
---

## Literature Review

# High Returns from Low Risk By Pim van Vliet and Jan De Koning
One of the most widely believed tenants of finance is the concept that with more risk comes more reward. However, looking at historical market returns, this does not appear to be the case. Over an 86-year period from 1929, low volatility stocks outperformed high volatility stocks by a factor of 18. If both portfolios started off with the same $100, the low volatility portfolio end value would be $395,000, while the high volatility portfolio would be worth just $21,000. Low risk stocks returned 10.2% annually whereas the high risk stocks returned just 6.4% annually. This difference of 3.8% is striking, and presents an anomaly in the field of finance.  

This begs the question of how a portfolio of lower volatility stocks can outperform higher volatility stocks over a long period of time. The primary way this occurs is that the low volatility portfolio loses less during times of financial stress. For example, in 1932 following the Great Depression, it was observed that the high volatility portfolio shrunk from $100 in value to $5 in value, while the low volatility portfolio shrunk from $100 to $30. Since the low volatility portfolio is able to lose less money, it is able to grow capital more effectively than the high volatility portfolio. In this example, the annualized volatility of the low risk portfolio was 13%, and the annualized volatility of the high risk portfolio was around 2.5 times that, at 36%. In addition to being more risky, the high volatility portfolio was outperformed by 18 times. 

Thus, it seems very counterintuitive that fund managers and investors would not only invest in low risk stocks. Part of understanding this comes from interpreting what risk is defined as in the financial community. Risk is not necessarily defined as losing money, as it may be for an individual, but instead underperforming a benchmark. Volatility is also an important concept to understand. Volatility is an important measure of financial risk, as it comes from the price fluctuations of a stock or investment. Volatility is also one of the best indicators of bankruptcy. Taking some risk does pay off, as the relationship between risk and return starts off slightly positive before leveling off and becoming negative. 
Many researchers focus on short-term periods when analyzing stock returns instead of longer term for a couple of reasons. The first reason many focus on “single period returns”, which in most academic studies is just a one month period, is because this takes away the significance of compounding. The longer the investment period, the more risk one takes in hurting long term returns through compounding. By not fully including the magic “return upon return” effect of compounding, a high-risk portfolio in this book performs more than 6% better per year. For example, if in month a portfolio worth $100 drops 50% to $50, then the next month increases 50% to $75, the investment return is dependent on how one divides the time period. Looking at it on a monthly basis, even though the portfolio lost $25, the net return would be -50% +50%, or 0%. Looking at it on a long term basis, the net return was -25%. 

David Blitz, the head of quantitative equity research at Robeco, discusses this different perspective as somewhat due to the need to benchmark the performance of an investment manager. This is a concept known as “relative” risk. In the examples above, everything has been in respect to absolute risk - that is how much money is being gained or lost due to overall stock movements, with regard to the starting amount of money invested. Volatility, in itself, captures these changes in the price of a stock, and is an absolute risk measurement. Many institutional investors do not look at risk on an absolute level, as a retiree or mom and pop investor may, but instead look at the risk of a portfolio with respect to market or some other widely accepted benchmark. For these investors, the risk is not as much about losing money, rather is more about lagging the market or their peers. Investing is very much a relative game. If a portfolio drops 20% while the market drops 40%, this is seen as a much better outcome than if a portfolio goes up 20% while the market goes up 40%. Thus, a portfolio that moves closely with the market has a very low relative risk. This risk can be calculated as volatility by looking at the relative price movements, instead of the absolute price movements. 

Investment professionals focus on relative risk for a number of reasons, one of which is the fact that they are not managing their own money. They need to prove to their bosses and clients that they are above average in their job. If a particular benchmark cannot be beaten by these investors, clients may ask why pay for them to manage their money when they could put it in a low-fee or no-fee mutual fund. This is one of the reasons that institutional investors need to compare their performance to some benchmark. Thus, the focus for investors is return and relative risk. Adding low risk stocks to the portfolio causes relative risk to increase a lot, making it an unappealing investment because low absolute risk inherently causes high relative risk. A low risk portfolio only makes sense if absolute risk is what one cares about. Thus, for those investors who don’t care about relative risk and just absolute risk, low risk stocks are a great investing opportunity.

In addition to the reasons mentioned, there are several additional reasons why some investors are not attracted to low-risk stocks. Eric Falkenstein, a renowned author in the low volatility investing realm, wrote that “envy is at the root of the investment paradox.” Some investors don’t recognize the significance of compounding returns. Others do, but are unable to utilize the paradox due to relative risk and career pressures. Analysts who choose big winners are more likely to get recognized than those who pick safer stocks with lower upside potential, and funds that pick the right high risk stocks also see more reward in an increase in AUM. Moreover, some people do not invest in low risk stocks because they have less appeal of high risk stocks, where they think they can make money easily and quickly. These high risk stocks are more “sexy” and have a “lottery ticket” element that attracts investors with the appeal of a big payday. 

# Betting Against Correlation: Testing Theories of the Low-Risk Effect

A recurring phenomena in finance, is the observation of the “low-risk effect.” This is the idea that lower risk or lower volatility stocks, tend to have higher alpha than higher risk or higher volatility stocks. In trying to understand the reason this anomaly occurs, are two possible explanations. The first looks at at whether this is caused by leverage constraints, meaning measurement using systematic risk. The second focuses on the behavioral effects, or idiosyncratic risks. One of the main issues with prior research, is that a lot of the low-risk factors are correlated and interrelated, making it hard to isolate certain factors or effects. In this paper, the global data was used, with a couple new factors meant to control for existing factors. 

Previous studies, like one by Adrian, Etula, and Muir in 2014, showed a link between return to the BAB (Betting Against Beta) factor and financial intermediary leverage. Many of these factors, though, including BAB, generally exhibit the “low-risk effect” and are thus very hard to differentiate between. Thus, this paper decided to do just that, by breaking down BAB into two other factors: betting against correlation (BAC) and betting against volatility (BAV). BAC is accomplished through longing stocks with low correlation to the market, and shorting those with high correlation to the market, while trying to match the volatilities of both the long and short portfolios. BAV is achieved in a similar manner, except instead of longing and shorting correlation, volatility is used, and correlation is kept constant. 

To address the behavioral explanation, the paper looks at some prior factors from studies done by Ang, Hodrick, Xing, and Zhang in 2006 and 2009. The first study found stocks with low idiosyncratic volatility (IVOL) have a greater risk-adjusted return, while the second found that a low maximum return (LMAX), a measure of idiosyncratic skewness, is associated with greater risk-adjusted returns. This paper kept the focus on LMAX and IVOL, but added another factor, scaled MAX (SMAX), which longs stocks with a low MAX return divided by ex ante volatility, and then shorts stocks with a high MAX return divided by ex ante volatility. This focuses on the lottery demand, holding volatility relatively constant and only focusing on the distribution of the returns. Margin debt held by investors, and investor sentiment were also noted. 

In the paper, 58,415 stocks from the MSCI World Index, from 24 countries between January 1926 and December 2015 were covered. BAB and BAC ended up being very successful in controlling for the other factors that could influence the “low-risk effect.” For all stocks, the BAC factor produced a significant six-factor alpha that was nearly independent of the other low-risk factors studied. In terms of explaining the behavioral side with factors, SMAX was the only truly great, resilient measure used. The rest generally had higher turnover, and were consequently very susceptible to microstructure noise. SMAX attained positive risk-adjusted returns in the U.S. but negative risk-adjusted returns globally, which was seen with some other idiosyncratic risk factors. The paper showed that systematic low-risk factor generally tended to outperform behavioral risk factors, especially when considering turnover and time period length.  All in all, the low-risk effect was believed to be driven by multiple factor effects, meaning both leverage constraints and the demand for lottery could play a role in effecting this. However, leverage constraint effects were a bit stronger, especially internationally.

# Price Response to Factor Index Additions and Deletions 

Some of the driving fundamental assumptions of finance is the flat demand curve for stocks, where risk is the main driver and each stock has a perfect substitute. However, this concept has been questioned for the past few years, with literature picking up on stocks with show supply shocks and checking how this affects their price. The literature has shown several instances where large block sales of stock has negatively affected its price. This was often due to information contamination, which is new, significant information about the company in the market. This information often reflects fundamental changes in the company, and if is is negative, will understandably trigger block sales. Thus, the price change is less due to the supply shock, and moreso due to the fundamental change in the company’s value (like a scandal or earnings report).

However, interesting patterns that have not yet been fully explained have been observed regarding S&P 500 company addition and deletions. When companies are added or removed from the index, it is purely mechanical, and usually not due to some drastic fundamental change in the company. Assuming the market is efficient, the demand for stocks should not change due to being added or removed from an index, but several studies have shown that it does. Harris and Gurel (1986), Shleifer (1986), Beneish and Whaley (1996), Chen, Noronha, and Singal (2004) all show how new additions to the S&P come with higher than normal returns for that company. Though they agree on the price movement, the studies tend to have a hard time agreeing on the reason for this price movement. Some possible explanations include compensation for providing liquidity, better monitoring for investors when a company is added to a reputable and large index, and higher analyst coverage leading to more information and analysis available on the company. One primary concern is whether or not index reshuffling is an information-free event - that is, whether a company being added or removed adds information to the market about the company. 

In this paper, the authors look at factor index rebalancing for an information-free event. Factor indices are part of a parent index of many other stocks, and are constructed in a mechanical way that is publically available and usually based on ranking stocks off a particular ratio of characteristic. Looking at the MSCI Minimum Volatility index, stocks returns were recorded for the stocks that had been added/dropped. It was found that the cumulative return from announcement to the effective day was 1.07% for stocks added with a significant t-statistic of 7.16, with 62% of the stocks exhibiting a positive cumulative abnormal return. Of the 1.07% increase, 0.63% of it was gained the following day, indicating that a large part of the increase is from an increase in demand from index funds. 0.31% of the return is lost five days after the rebalancing, but generally the price tends to stabilize afterwards after ten days. Thus, 68% of the price increase is permanent, while the other 32% is temporary and lost after a few days. This can be due to a number of reasons including a liquidity premium charged by the stock’s owner or arbitrage activity. Average trading volume was also significantly more for stocks that were recently added to the index. Between the announcement and actual day of adding the stock, the average trading volume was 30% higher than normal, with a significant t-statistic of 3.81. Moreover, there is a 74% increase in volume for the day prior to the actual adding of the security. A very similar phenomena occurs with stocks set to be dropped from the MSCI Minimum Volatility Index. From the announcement of a stock being dropped to the day before it is actually deleted from the index, the total cumulative abnormal return is -0.91%, and -0.57% of this comes the day right before. After the stocks are deleted, 64% of them have a negative return the following day, and only 0.49% of the -0.91% is regained after three weeks. Trading volume also spikes 46% on the day prior to removal from the index. After three weeks, it returns back to within 1% of the normal trading volume.

These findings imply that once a security is added to a factor index, the demand curve shifts to the right, moving the equilibrium. The trading volume change is likely due to index funds buying or selling massive amounts of the stocks that will be added or removed. Moreover, it was found that the amount of the return is also directly related to the weighting of the volume of stocks entering or leaving the factor index. All in all, these findings suggest an index arbitrage opportunity if the index additions or deletions can be predicted.

# Benchmarks as Limits to Arbitrage: Understanding the Low-Volatility Anomaly
Low-beta and low-volatility stocks have outperformed high-beta, high-volatility stocks from 1968-2008, combining great returns with low downturns. This can be explained by behavioral models of security prices. First is the idea that investors have a preference for “lotteries” and a bias of overconfidence creates a higher demand for higher-volatility securities. Second is the idea that this arbitrage opportunity is very limited, as the need to benchmark creates a greater demand for higher risk stocks, while discouraging investments in low-beta, low-volatility stocks. Several other papers have tried to explain this seemingly misunderstood phenomena, including Karceski in 2002, where is was noted that an extrapolation bias could cause mutual fund managers to care more about overperforming in a bull market, than underperforming in a bear market. This understandably, increases the market’s appetite for risky stocks with high reward potential. This paper focuses on the distortions caused specifically by benchmarking.

In the paper, the authors used 41 years of CRSP data, ranging from January 1968 – December 2008. Using the top 1,000 stocks by market cap, the five year trailing volatilities were calculated and returns were tracked. A dollar investment from 1968 made its way to $59.55, or $10.12 in real terms when accounting for inflation. On the other hand, the highest volatility portfolio went from a dollar in value to 58 cents during the period, with a real value of just around 10 cents when considering inflation. When using beta as a measure for risk, the finding was very similar. In the lowest-beta portfolio, a dollar grew to $60.46 in nominal value, or $10.28 in real value after inflation. The highest-beta portfolio grew from a dollar to $3.77 in nominal terms, or $0.64 in real terms after inflation. This held true for large cap companies, but the discrepancy was even higher for smaller cap companies. Generally, the low-risk portfolios also grew much more steadily and constant, without many drawdowns. To add on to this as well, the portfolio values did not include transaction costs. The high-risk portfolios cost more to rebalance on a monthly level, as was done in the paper, than the low-risk portfolios, indicating this anomaly is more pronounced that initially reported. These findings are not novel, but this paper attempts to explain them in a new way. Many theories add evidence for disproving the Capital Asset Pricing Model (CAPM), and even suggest that beta may not be the correct measure of risk. Other models relating risk and return, however, have had difficulty gaining acceptance and widespread usage in the finance industry. 

One theory explored in detail is an investor’s irrational preference for high-volatility stocks. First, many investors have a natural preference for lotteries, even though there is a general aversion towards loss. If a stock has a positive skew, that is a larger probability of a large positive payoff than probability of a small payoff, investors typically are very interested. Though skew is not the same as volatility, in their paper in 2010, Boyer, Mitton, and Vorkink make a strong case for how expected skewness is a proxy for volatility. Another idea is representativeness, or that Bayes’ rule and probability theory are often not natural to people. One example of this is, selectively looking at a few speculative investments that have turned out to be massive successes, without considering the numerous failures. Overconfidence has also been tied to a preference for volatile stocks; optimists are generally more aggressive than pessimists. 

The need for benchmarking, especially among institutional investors, is also believed to heavily play into the anomaly. In fact, from the period when institutional investors managed 30% of all money to 60%, the anomaly intensified. This still begs the question as to why institutional investors do not buy more low-volatility stocks, and the answer has to do with benchmarking. The typical fund manager is judged for his/her “information ratio” (IR) which is the expected return difference between the manager and the expected return of the S&P 500, divided by the volatility of this return difference (tracking error). The goal of the investment manager is to maximize this information ratio, best as possible, through picking stocks. In 2009, Sensoy showed that over 61% of U.S. mutual fund managers are benchmarked against the S&P 500, while over 94% are benchmarked to some U.S. index benchmark. Moreover, SEC rules require mutual funds to compare their performance to some benchmark. This intuitively makes sense, as it allows investors to assess the skill and ability of managers in an unbiased way, and also allows fund managers a chance to differentiate themselves. 

Investment managers without leverage will try to find mispriced stocks with a beta very close to market risk (beta of 1), overweighting positive-alpha stocks while underweighting negative-alpha stocks. When comparing the Sharpe ratio of large cap stocks for a low-volatility portfolio, it was quite high at 0.38. However, IR was a very low 0.08, showing this would be very tough for a fund manager to invest in. While Beta and volatility are undoubtedly very correlated, the study showed that beta is more related to the anomaly than volatility, especially with large cap stocks, which is what most fund managers disproportionately focus their invests in. Both volatility and beta play a significant role in this anomaly in smaller cap stocks. Looking at the period from 1968-2008, the top value strategy portfolios had an IR of 0.51, and top momentum strategy portfolios had an IR of 0.64. This is extremely high compared to the IR of low-volatility stocks in this period, which ranged from 0.08 to 0.17. 

Overall, irrational investor preference for lotteries and high volatility stocks, as well as investment managers’ focus on benchmarks and IR flatten or even invert the relationship between risk and return as we know it. This has been shown by the study, and prior observations that the anomaly intensified with the increase in AUM of fund managers in the U.S. These reasons appear perennial, so the anomaly will likely not be going away anytime soon. One other factor to this is compounding of the low-volatility portfolio. Since it suffers fewer drawdowns, this means the portfolio is able to experience more stable and upward growth. 

# Betting Against Beta
In this paper, a real-world resembling model is created with leverage and margin constraints in 55,600 stocks from 20 global stock, bond, credit, and futures markets. Some agents in this model cannot use any leverage, and some have limited margin constraints, much like many investors and fund managers. 

Many mutual funds, pension funds, and individual investors are constrained by the amount of leverage they can take on, such that instead of investing in a portfolio yielding the highest Sharpe Ratio, they are forced to overweight portfolios with higher risk stocks. This suggests fund managers hold high-beta stocks to a lower risk adjusted return standard than low-beta stocks, which would require leverage. Thus, if one cannot leverage or has significant leverage constraints, then this agent will overweight riskier securities. The model was able to empirically show this in the equities, bonds, and futures markets. This was done by sorting portfolios by betas, and realizing alphas and sharpe ratios declining with increases in portfolio beta. 

Moreover, if one can leverage without constraint, then they would underweight high-beta assets and overweight low-beta assets. Betting against beta (BAB) factors help explain this better. A BAB factor is a portfolio longing low-beta securities (leveraged to a beta of 1), shorting high-beta assets (deleveraged to a beta of 1). Hence, a BAB factor is market neutral. The model in the paper predicts that this portfolio will have a positive return, that increases with the spread in the betas and tightness of leverage constraints. Thus, longing low-beta and shorting high-beta yields significant, and positive risk-adjusted returns. This was observed in the model by looking at U.S., developing, and international equity markets and observing that the BAB factor yielded a Sharpe ratio that was double its value effect, and 40% greater than momentum. The BAB factor had very high risk adjusted returns, and during four twenty-year periods between 1926 and 2012, produced significant positive returns. This generally held across other asset classes, including credit and treasury bond markets. 

When a leverage constraint is met or surpassed, and the agent needs to deleverage, the BAB factor portfolio experiences negative returns, but its expected future returns increase. This was once again shown with a time series with spreads of various funding constraints. 

Another central idea of the model was that increased funding liquidity risk compresses betas toward one. This was proven by looking at the volatility of funding constraints as funding liquidity risk, and the end result was that the dispersion of betas when funding liquidity risk is high, was much lower than when funding liquidity risk is low. 

Finally, the model showed that investors that are more constrained are forced to overweight riskier securities, while investors without such constraints can overweight lower-risk securities. Studying a number of stock portfolios from constrained investors, most fund managers and individual investors’ portfolios have a beta greater than one. On the flip side, many PE firms that perform an LBO get firms with a beta below one, and apply leverage. Great investor Warren Buffett even bets against beta, as many of his investments are leveraged, low-beta stocks.

# MSCI Min Vol Index Information
The MSCI Minimum Volatility Index (USMV) is intended to have a lower beta, lower volatility, lower cap bias, and contain more stocks with less risk than its parent index. It is rebalanced twice a year, on the last trading days of May and November. The index typically has around 180 constituents, with an average of 20 new additions and 14 deletions every 6 months when rebalancing occurs. Over the last five, years, the number of additions has ranged from 12 to 25, while the deletions have been between 10 and 19. Changes to the index are usually announced nine trading days before they are set to take place. 

Using the Barra Open Optimizer, USMV creates a minimum variance portfolio of low risk stocks, as a subset from its parent index, EUSA. Using this estimated security covariance matrix, the MSCI Minimum Volatility Index is the product of the lowest absolute volatility, considering the constraints.  Moreover, these additions are simply a relabeling of existing stocks in the parent index, and do not include new additions to the parent index. The low-risk stocks chosen to be in USMV are determined by a set of constraints, like maintaining a certain sector or country weight relative to the parent index.  

There are many specific constraints to this index. The first is that an individual stock cannot exceed 1.5% or 20 times the weight of the stock in the parent index. The minimum weight of a security in the index is also capped at 0.05%. USMV also aims to keep the weight of specific countries within a 5% range of the weight in the parent index, or 3 times the weight of the country in the parent index. Sector weights of USMV also cannot deviate more than 5% from the sector weights in the parent index. One way turnover of the index is also maxed at 10%. Thus, taking into account these constraints, the Barra Open Optimizer creates the lowest absolute volatility portfolio possible. 


# The Low-Risk Anomaly: A Decomposition into Micro and Macro Effects
The low beta anomaly can be broken up into micro and macro effects. The micro effects include picking low beta stocks, while the macro effects are picking low beta countries or industries. In this paper, the micro effects were recorded by creating long-short portfolios of stocks, holding constant country and industry risk. The macro effects were observed through long-short portfolios of various countries and industries, holding stock level risk constant. Studying a number of stocks within 29 industries and 31 different developed countries, the macro and micro effects were observed, and both together were shown to play an important role in the low risk anomaly. 

Micro selection of stocks, that is constructing a low risk portfolio of stocks, holding country and industry constant, showed that risk could be significantly decreased without a significant decrease in return. Macro selection, especially with regards to the country chosen, causes greater returns with small differences in risk. These findings have pretty significant implications, as this indicates that people seeking arbitrage opportunities through mispricing of industry or sector ETFs may not be as feasible or profitable as one may think. There is more of an opportunity exploiting the micro effects of individual stock selection. 

It was found that using industry beta to predict future stock betas was possible, but not as effective as just using historical stock betas. However, industry beta information without stock information does improve risk-adjusted returns, just not as to the same level as with stock information. The paper also goes into detail trying to isolate pure industry effects and pure stock effects. Pure industry effects are the average differences between high and low beta industries, while holding constant stock risk. Pure stock risk is the opposite of that, calculating the average difference between high bet and low beta stocks, keeping industry risk constant. In the end, finding low-risk portfolios using selection of low risk stocks keeping industry constant was around four times more effective than using industries and keeping stock risk constant. Using the historical betas of both together, however, has more predictive power than either one alone. 

Next, looking at 31 developed countries including Canada, France, Germany, Japan, and Singapore, the paper worked to decompose the low risk anomaly into country and stock specific effects. Similar to the industry findings, country beta was able to predict stock betas to a certain extent, but not as well as historical stock betas were. Looking only at country betas yielded around half the risk reduction and two-thirds the risk adjusted return improvement, as compared to stock betas. This study implies that predicting risk of individual stocks is in itself very hard when only given data on country or industry risk, but when given all the data can have much more predictive power. 

# Data Analysis
Data was collected from data on ishares.com, and compiled from 10/31/2011 to 1/5/2017.
```{r}
# Load Packages and View the Data
library(mscidata)
library(ggplot2)
data(usa)
data(minvol)

## Summary statistics of EUSA Data
head(usa)
tail(usa)
summary(usa)

## Summary statistics of USMV Data
head(minvol)
tail(minvol)
summary(minvol)
```

Next, sector weights were calculated over time for both EUSA and USMV. Plots were made by sector and displayed to compare the relative weights of EUSA and USMV. 
```{r}
data(usa_percent)
data(minvol_percent)

## Summary statistics of EUSA sector weights
head(usa_percent)
tail(usa_percent)
summary(usa_percent)

## Summary statistics of USMV sector weights
head(minvol_percent)
tail(minvol_percent)
summary(minvol_percent)
```

# EUSA and USMV weightings by Sector
```{r, echo = FALSE}
## Energy
Eng1 <- usa_percent[which(usa_percent$sector_name=="Energy"), ]
Eng2 <- minvol_percent[which(minvol_percent$sector_name=="Energy"), ]
ggplot(Eng1, aes(date, percent, colour = "USA")) + geom_line() +  
ggtitle("USA vs. Min Vol Energy Sector Weights") + xlab("Time") + ylab("Sector Weight") +
geom_line(data = Eng2, aes(x=date, y=percent, colour="Min Vol"),show.legend = TRUE)

## Finacials
Fin1 <- usa_percent[which(usa_percent$sector_name=="Financials"), ]
Fin2 <- minvol_percent[which(minvol_percent$sector_name=="Financials"), ]
ggplot(Fin1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Financial Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + 
geom_line(data = Fin2, aes(x=date, y=percent, colour="Min Vol"),show.legend = TRUE)

## Consumer Staples
ConStap1 <- usa_percent[which(usa_percent$sector_name=="Consumer Staples"), ]
ConStap2 <- minvol_percent[which(minvol_percent$sector_name=="Consumer Staples"), ]
ggplot(ConStap1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Consumer Staples Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = ConStap2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Consumer Discretionary
ConDis1 <- usa_percent[which(usa_percent$sector_name=="Consumer Discretionary"), ]
ConDis2 <- minvol_percent[which(minvol_percent$sector_name=="Consumer Discretionary"), ]
ggplot(ConDis1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Consumer Discretionary Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = ConDis2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Health Care
Health1 <- usa_percent[which(usa_percent$sector_name=="Health Care"), ]
Health2 <- minvol_percent[which(minvol_percent$sector_name=="Health Care"), ]
ggplot(Health1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Health Care Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Health2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Industrials
Ind1 <- usa_percent[which(usa_percent$sector_name=="Industrials"), ]
Ind2 <- minvol_percent[which(minvol_percent$sector_name=="Industrials"), ]
ggplot(Ind1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Industrials Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Ind2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Information Technology
IT1 <- usa_percent[which(usa_percent$sector_name=="Information Technology"), ]
IT2 <- minvol_percent[which(minvol_percent$sector_name=="Information Technology"), ]
ggplot(IT1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Information Technology Sector Weights") + 
xlab("Time") + ylab("Sector Weight") + geom_line(data = IT2, aes(x=date, y=percent,
colour="Min Vol"),show.legend = TRUE)

## Materials
Mat1 <- usa_percent[which(usa_percent$sector_name=="Materials"), ]
Mat2 <- minvol_percent[which(minvol_percent$sector_name=="Materials"), ]
ggplot(Mat1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Materials Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Mat2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Utilites
Util1 <- usa_percent[which(usa_percent$sector_name=="Utilities"), ]
Util2 <- minvol_percent[which(minvol_percent$sector_name=="Utilities"), ]
ggplot(Util1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Utilities Sector Weights") + xlab("Time") + 
ylab("Sector Weight") + geom_line(data = Util2, aes(x=date, y=percent, 
colour="Min Vol"),show.legend = TRUE)

## Telecommunication Services
Telecom1 <- usa_percent[which(usa_percent$sector_name=="Telecommunications"), ]
Telecom2 <- minvol_percent[which(minvol_percent$sector_name=="Telecommunications"), ]
ggplot(Telecom1, aes(date, percent, colour = "USA")) + geom_line() + 
ggtitle("USA vs. Min Vol Telecommunications Services Sector Weights") + 
xlab("Time") + ylab("Sector Weight") + geom_line(data = Telecom2, aes(x=date, 
y=percent, colour="Min Vol"),show.legend = TRUE)
```

# USMV WRDS Data
10-years of data, from 10/04/2010 to 12/30/2016, was collected from WRDS for the 300 historical constituents of the MSCI Minimum Volatility Index (USMV), to find their 252-day (annual) trailing volatility. 
```{r, echo = FALSE}
library(ggplot2)
library(mscidata)

#AAP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AAP, aes(Date, SD)) + ggtitle("AAP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ABBV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ABBV, aes(Date, SD)) + ggtitle("ABBV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ABC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ABC, aes(Date, SD)) + ggtitle("ABC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ABT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ABT, aes(Date, SD)) + ggtitle("ABT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ACE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ACE, aes(Date, SD)) + ggtitle("ACE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ACGL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ACGL, aes(Date, SD)) + ggtitle("ACGL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ACN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ACN, aes(Date, SD)) + ggtitle("ACN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ADBE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ADBE, aes(Date, SD)) + ggtitle("ADBE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ADP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ADP, aes(Date, SD)) + ggtitle("ADP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AEP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AEP, aes(Date, SD)) + ggtitle("AEP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AET 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AET, aes(Date, SD)) + ggtitle("AET 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AGN, aes(Date, SD)) + ggtitle("AGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AGNC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AGNC, aes(Date, SD)) + ggtitle("AGNC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ALL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ALL, aes(Date, SD)) + ggtitle("ALL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ALTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ALTR, aes(Date, SD)) + ggtitle("ALTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AMGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AMGN, aes(Date, SD)) + ggtitle("AMGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AMT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AMT, aes(Date, SD)) + ggtitle("AMT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ANSS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ANSS, aes(Date, SD)) + ggtitle("ANSS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ANTM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ANTM, aes(Date, SD)) + ggtitle("ANTM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AON 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AON, aes(Date, SD)) + ggtitle("AON 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#APH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(APH, aes(Date, SD)) + ggtitle("APH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AR, aes(Date, SD)) + ggtitle("AR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ARMK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ARMK, aes(Date, SD)) + ggtitle("ARMK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ATVI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ATVI, aes(Date, SD)) + ggtitle("ATVI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AVB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AVB, aes(Date, SD)) + ggtitle("AVB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AWK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AWK, aes(Date, SD)) + ggtitle("AWK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AXS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AXS, aes(Date, SD)) + ggtitle("AXS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#AZO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(AZO, aes(Date, SD)) + ggtitle("AZO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BAX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BAX, aes(Date, SD)) + ggtitle("BAX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BBBY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BBBY, aes(Date, SD)) + ggtitle("BBBY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BCR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BCR, aes(Date, SD)) + ggtitle("BCR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BDX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BDX, aes(Date, SD)) + ggtitle("BDX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BIIB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BIIB, aes(Date, SD)) + ggtitle("BIIB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BMC, aes(Date, SD)) + ggtitle("BMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BMY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BMY, aes(Date, SD)) + ggtitle("BMY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BR, aes(Date, SD)) + ggtitle("BR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BRX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BRX, aes(Date, SD)) + ggtitle("BRX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BSX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BSX, aes(Date, SD)) + ggtitle("BSX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BXLT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BXLT, aes(Date, SD)) + ggtitle("BXLT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#BXP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(BXP, aes(Date, SD)) + ggtitle("BXP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CA, aes(Date, SD)) + ggtitle("CA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CAG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CAG, aes(Date, SD)) + ggtitle("CAG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CAH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CAH, aes(Date, SD)) + ggtitle("CAH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CB, aes(Date, SD)) + ggtitle("CB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CCI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CCI, aes(Date, SD)) + ggtitle("CCI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CDNS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CDNS, aes(Date, SD)) + ggtitle("CDNS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CELG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CELG, aes(Date, SD)) + ggtitle("CELG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CHD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CHD, aes(Date, SD)) + ggtitle("CHD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CHRW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CHRW, aes(Date, SD)) + ggtitle("CHRW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CHTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CHTR, aes(Date, SD)) + ggtitle("CHTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CI, aes(Date, SD)) + ggtitle("CI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CINF 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CINF, aes(Date, SD)) + ggtitle("CINF 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CL, aes(Date, SD)) + ggtitle("CL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CLX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CLX, aes(Date, SD)) + ggtitle("CLX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CMCSA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CMCSA, aes(Date, SD)) + ggtitle("CMCSA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CMCSK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CMCSK, aes(Date, SD)) + ggtitle("CMCSK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CME 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CME, aes(Date, SD)) + ggtitle("CME 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CMG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CMG, aes(Date, SD)) + ggtitle("CMG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COG, aes(Date, SD)) + ggtitle("COG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COLE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COLE, aes(Date, SD)) + ggtitle("COLE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COO, aes(Date, SD)) + ggtitle("COO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COP, aes(Date, SD)) + ggtitle("COP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COST 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COST, aes(Date, SD)) + ggtitle("COST 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#COV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(COV, aes(Date, SD)) + ggtitle("COV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CPB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CPB, aes(Date, SD)) + ggtitle("CPB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CPT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CPT, aes(Date, SD)) + ggtitle("CPT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CRC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CRC, aes(Date, SD)) + ggtitle("CRC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CSCO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CSCO, aes(Date, SD)) + ggtitle("CSCO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CTAS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CTAS, aes(Date, SD)) + ggtitle("CTAS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CTL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CTL, aes(Date, SD)) + ggtitle("CTL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CVS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CVS, aes(Date, SD)) + ggtitle("CVS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#CVX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(CVX, aes(Date, SD)) + ggtitle("CVX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#D 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(D, aes(Date, SD)) + ggtitle("D 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DD, aes(Date, SD)) + ggtitle("DD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DE, aes(Date, SD)) + ggtitle("DE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DG, aes(Date, SD)) + ggtitle("DG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DGX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DGX, aes(Date, SD)) + ggtitle("DGX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DHR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DHR, aes(Date, SD)) + ggtitle("DHR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DIS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DIS, aes(Date, SD)) + ggtitle("DIS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DLR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DLR, aes(Date, SD)) + ggtitle("DLR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DLTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DLTR, aes(Date, SD)) + ggtitle("DLTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DNB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DNB, aes(Date, SD)) + ggtitle("DNB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DPS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DPS, aes(Date, SD)) + ggtitle("DPS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DRI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DRI, aes(Date, SD)) + ggtitle("DRI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DTV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DTV, aes(Date, SD)) + ggtitle("DTV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DUK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DUK, aes(Date, SD)) + ggtitle("DUK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#DVA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(DVA, aes(Date, SD)) + ggtitle("DVA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EBAY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EBAY, aes(Date, SD)) + ggtitle("EBAY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ECL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ECL, aes(Date, SD)) + ggtitle("ECL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ED 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ED, aes(Date, SD)) + ggtitle("ED 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EFX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EFX, aes(Date, SD)) + ggtitle("EFX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EGN, aes(Date, SD)) + ggtitle("EGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EMC, aes(Date, SD)) + ggtitle("EMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EQR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EQR, aes(Date, SD)) + ggtitle("EQR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ES 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ES, aes(Date, SD)) + ggtitle("ES 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ESRX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ESRX, aes(Date, SD)) + ggtitle("ESRX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ESS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ESS, aes(Date, SD)) + ggtitle("ESS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EW, aes(Date, SD)) + ggtitle("EW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EXPD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EXPD, aes(Date, SD)) + ggtitle("EXPD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#EXR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(EXR, aes(Date, SD)) + ggtitle("EXR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FB, aes(Date, SD)) + ggtitle("FB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FDO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FDO, aes(Date, SD)) + ggtitle("FDO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FIS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FIS, aes(Date, SD)) + ggtitle("FIS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FISV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FISV, aes(Date, SD)) + ggtitle("FISV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FL, aes(Date, SD)) + ggtitle("FL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FNF 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FNF, aes(Date, SD)) + ggtitle("FNF 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FRC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FRC, aes(Date, SD)) + ggtitle("FRC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FRT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FRT, aes(Date, SD)) + ggtitle("FRT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FRX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FRX, aes(Date, SD)) + ggtitle("FRX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FTR, aes(Date, SD)) + ggtitle("FTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#FTV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(FTV, aes(Date, SD)) + ggtitle("FTV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GAS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GAS, aes(Date, SD)) + ggtitle("GAS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GD, aes(Date, SD)) + ggtitle("GD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GGP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GGP, aes(Date, SD)) + ggtitle("GGP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GILD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GILD, aes(Date, SD)) + ggtitle("GILD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GIS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GIS, aes(Date, SD)) + ggtitle("GIS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GOOG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GOOG, aes(Date, SD)) + ggtitle("GOOG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GOOGL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GOOGL, aes(Date, SD)) + ggtitle("GOOGL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GPC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GPC, aes(Date, SD)) + ggtitle("GPC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GR, aes(Date, SD)) + ggtitle("GR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#GWW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(GWW, aes(Date, SD)) + ggtitle("GWW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HCN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HCN, aes(Date, SD)) + ggtitle("HCN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HCP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HCP, aes(Date, SD)) + ggtitle("HCP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HD, aes(Date, SD)) + ggtitle("HD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HNZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HNZ, aes(Date, SD)) + ggtitle("HNZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HOLX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HOLX, aes(Date, SD)) + ggtitle("HOLX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HRL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HRL, aes(Date, SD)) + ggtitle("HRL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HSIC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HSIC, aes(Date, SD)) + ggtitle("HSIC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HSY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HSY, aes(Date, SD)) + ggtitle("HSY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#HUM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(HUM, aes(Date, SD)) + ggtitle("HUM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#IBM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(IBM, aes(Date, SD)) + ggtitle("IBM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#IHS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(IHS, aes(Date, SD)) + ggtitle("IHS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#INCO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(INCO, aes(Date, SD)) + ggtitle("INCO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#INTC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(INTC, aes(Date, SD)) + ggtitle("INTC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#INTU 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(INTU, aes(Date, SD)) + ggtitle("INTU 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ISRG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ISRG, aes(Date, SD)) + ggtitle("ISRG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#IT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(IT, aes(Date, SD)) + ggtitle("IT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#JBHT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(JBHT, aes(Date, SD)) + ggtitle("JBHT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#JNJ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(JNJ, aes(Date, SD)) + ggtitle("JNJ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#JWN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(JWN, aes(Date, SD)) + ggtitle("JWN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#K 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(K, aes(Date, SD)) + ggtitle("K 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KFT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KFT, aes(Date, SD)) + ggtitle("KFT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KMB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KMB, aes(Date, SD)) + ggtitle("KMB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KMI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KMI, aes(Date, SD)) + ggtitle("KMI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KMR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KMR, aes(Date, SD)) + ggtitle("KMR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KO, aes(Date, SD)) + ggtitle("KO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#KRFT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(KRFT, aes(Date, SD)) + ggtitle("KRFT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LB, aes(Date, SD)) + ggtitle("LB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LDOS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LDOS, aes(Date, SD)) + ggtitle("LDOS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LH, aes(Date, SD)) + ggtitle("LH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LIFE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LIFE, aes(Date, SD)) + ggtitle("LIFE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LLTC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LLTC, aes(Date, SD)) + ggtitle("LLTC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LLY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LLY, aes(Date, SD)) + ggtitle("LLY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LMT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LMT, aes(Date, SD)) + ggtitle("LMT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LO, aes(Date, SD)) + ggtitle("LO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LOW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LOW, aes(Date, SD)) + ggtitle("LOW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#LUV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(LUV, aes(Date, SD)) + ggtitle("LUV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MA, aes(Date, SD)) + ggtitle("MA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MAC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MAC, aes(Date, SD)) + ggtitle("MAC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MAT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MAT, aes(Date, SD)) + ggtitle("MAT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MCD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MCD, aes(Date, SD)) + ggtitle("MCD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MCK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MCK, aes(Date, SD)) + ggtitle("MCK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MDLZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MDLZ, aes(Date, SD)) + ggtitle("MDLZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MDT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MDT, aes(Date, SD)) + ggtitle("MDT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MHFI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MHFI, aes(Date, SD)) + ggtitle("MHFI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MKC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MKC, aes(Date, SD)) + ggtitle("MKC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MKL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MKL, aes(Date, SD)) + ggtitle("MKL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MMC, aes(Date, SD)) + ggtitle("MMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MMM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MMM, aes(Date, SD)) + ggtitle("MMM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MNK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MNK, aes(Date, SD)) + ggtitle("MNK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MO, aes(Date, SD)) + ggtitle("MO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MON 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MON, aes(Date, SD)) + ggtitle("MON 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MRK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MRK, aes(Date, SD)) + ggtitle("MRK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MSFT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MSFT, aes(Date, SD)) + ggtitle("MSFT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MSI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MSI, aes(Date, SD)) + ggtitle("MSI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#MTB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(MTB, aes(Date, SD)) + ggtitle("MTB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NEE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NEE, aes(Date, SD)) + ggtitle("NEE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NEM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NEM, aes(Date, SD)) + ggtitle("NEM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NKE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NKE, aes(Date, SD)) + ggtitle("NKE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NLSN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NLSN, aes(Date, SD)) + ggtitle("NLSN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NLY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NLY, aes(Date, SD)) + ggtitle("NLY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NNN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NNN, aes(Date, SD)) + ggtitle("NNN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NOC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NOC, aes(Date, SD)) + ggtitle("NOC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NST 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NST, aes(Date, SD)) + ggtitle("NST 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#NWSA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(NWSA, aes(Date, SD)) + ggtitle("NWSA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#O 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(O, aes(Date, SD)) + ggtitle("O 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#OCR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(OCR, aes(Date, SD)) + ggtitle("OCR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#OMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(OMC, aes(Date, SD)) + ggtitle("OMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ORCL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ORCL, aes(Date, SD)) + ggtitle("ORCL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ORLY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ORLY, aes(Date, SD)) + ggtitle("ORLY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#OXY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(OXY, aes(Date, SD)) + ggtitle("OXY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PAYX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PAYX, aes(Date, SD)) + ggtitle("PAYX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PBCT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PBCT, aes(Date, SD)) + ggtitle("PBCT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PCG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PCG, aes(Date, SD)) + ggtitle("PCG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PCP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PCP, aes(Date, SD)) + ggtitle("PCP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PDCO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PDCO, aes(Date, SD)) + ggtitle("PDCO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PEP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PEP, aes(Date, SD)) + ggtitle("PEP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PETM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PETM, aes(Date, SD)) + ggtitle("PETM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PFE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PFE, aes(Date, SD)) + ggtitle("PFE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PG, aes(Date, SD)) + ggtitle("PG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PGN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PGN, aes(Date, SD)) + ggtitle("PGN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PGR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PGR, aes(Date, SD)) + ggtitle("PGR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PM, aes(Date, SD)) + ggtitle("PM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#POM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(POM, aes(Date, SD)) + ggtitle("POM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PRE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PRE, aes(Date, SD)) + ggtitle("PRE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PRGO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PRGO, aes(Date, SD)) + ggtitle("PRGO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PSA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PSA, aes(Date, SD)) + ggtitle("PSA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PSX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PSX, aes(Date, SD)) + ggtitle("PSX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PX, aes(Date, SD)) + ggtitle("PX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#PYPL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(PYPL, aes(Date, SD)) + ggtitle("PYPL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#Q 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(Q, aes(Date, SD)) + ggtitle("Q 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#QCOM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(QCOM, aes(Date, SD)) + ggtitle("QCOM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RAI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RAI, aes(Date, SD)) + ggtitle("RAI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RE, aes(Date, SD)) + ggtitle("RE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#REG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(REG, aes(Date, SD)) + ggtitle("REG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RMD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RMD, aes(Date, SD)) + ggtitle("RMD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RNR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RNR, aes(Date, SD)) + ggtitle("RNR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ROST 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ROST, aes(Date, SD)) + ggtitle("ROST 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RSG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RSG, aes(Date, SD)) + ggtitle("RSG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#RTN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(RTN, aes(Date, SD)) + ggtitle("RTN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SBAC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SBAC, aes(Date, SD)) + ggtitle("SBAC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SBUX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SBUX, aes(Date, SD)) + ggtitle("SBUX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SE, aes(Date, SD)) + ggtitle("SE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SHW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SHW, aes(Date, SD)) + ggtitle("SHW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SIAL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SIAL, aes(Date, SD)) + ggtitle("SIAL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SJM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SJM, aes(Date, SD)) + ggtitle("SJM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SLB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SLB, aes(Date, SD)) + ggtitle("SLB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SNI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SNI, aes(Date, SD)) + ggtitle("SNI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SNPS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SNPS, aes(Date, SD)) + ggtitle("SNPS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SO, aes(Date, SD)) + ggtitle("SO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SPG 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SPG, aes(Date, SD)) + ggtitle("SPG 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SRCL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SRCL, aes(Date, SD)) + ggtitle("SRCL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SRE 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SRE, aes(Date, SD)) + ggtitle("SRE 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#STJ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(STJ, aes(Date, SD)) + ggtitle("STJ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#STZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(STZ, aes(Date, SD)) + ggtitle("STZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SYK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SYK, aes(Date, SD)) + ggtitle("SYK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SYMC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SYMC, aes(Date, SD)) + ggtitle("SYMC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#SYY 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(SYY, aes(Date, SD)) + ggtitle("SYY 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#T 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(T, aes(Date, SD)) + ggtitle("T 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TGT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TGT, aes(Date, SD)) + ggtitle("TGT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TJX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TJX, aes(Date, SD)) + ggtitle("TJX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TMO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TMO, aes(Date, SD)) + ggtitle("TMO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TRV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TRV, aes(Date, SD)) + ggtitle("TRV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TSS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TSS, aes(Date, SD)) + ggtitle("TSS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#TXN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(TXN, aes(Date, SD)) + ggtitle("TXN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UDR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UDR, aes(Date, SD)) + ggtitle("UDR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UHS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UHS, aes(Date, SD)) + ggtitle("UHS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ULTA 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ULTA, aes(Date, SD)) + ggtitle("ULTA 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UNH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UNH, aes(Date, SD)) + ggtitle("UNH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UNP 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UNP, aes(Date, SD)) + ggtitle("UNP 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UPS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UPS, aes(Date, SD)) + ggtitle("UPS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#USB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(USB, aes(Date, SD)) + ggtitle("USB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#USD 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(USD, aes(Date, SD)) + ggtitle("USD 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#UTX 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(UTX, aes(Date, SD)) + ggtitle("UTX 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#V 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(V, aes(Date, SD)) + ggtitle("V 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VAL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VAL, aes(Date, SD)) + ggtitle("VAL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VAR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VAR, aes(Date, SD)) + ggtitle("VAR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VFC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VFC, aes(Date, SD)) + ggtitle("VFC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VMW 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VMW, aes(Date, SD)) + ggtitle("VMW 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VNO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VNO, aes(Date, SD)) + ggtitle("VNO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VNTV 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VNTV, aes(Date, SD)) + ggtitle("VNTV 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VRSK 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VRSK, aes(Date, SD)) + ggtitle("VRSK 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VRSN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VRSN, aes(Date, SD)) + ggtitle("VRSN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VTR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VTR, aes(Date, SD)) + ggtitle("VTR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#VZ 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(VZ, aes(Date, SD)) + ggtitle("VZ 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WAT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WAT, aes(Date, SD)) + ggtitle("WAT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WCN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WCN, aes(Date, SD)) + ggtitle("WCN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WEC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WEC, aes(Date, SD)) + ggtitle("WEC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WFC 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WFC, aes(Date, SD)) + ggtitle("WFC 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WIN 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WIN, aes(Date, SD)) + ggtitle("WIN 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WM, aes(Date, SD)) + ggtitle("WM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WMT 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WMT, aes(Date, SD)) + ggtitle("WMT 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WPI 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WPI, aes(Date, SD)) + ggtitle("WPI 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WR 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WR, aes(Date, SD)) + ggtitle("WR 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WRB 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WRB, aes(Date, SD)) + ggtitle("WRB 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#WSH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(WSH, aes(Date, SD)) + ggtitle("WSH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#XEL 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(XEL, aes(Date, SD)) + ggtitle("XEL 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#XOM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(XOM, aes(Date, SD)) + ggtitle("XOM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#Y 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(Y, aes(Date, SD)) + ggtitle("Y 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#YHOO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(YHOO, aes(Date, SD)) + ggtitle("YHOO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#YUM 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(YUM, aes(Date, SD)) + ggtitle("YUM 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ZAYO 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ZAYO, aes(Date, SD)) + ggtitle("ZAYO 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ZBH 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ZBH, aes(Date, SD)) + ggtitle("ZBH 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

#ZTS 252-day Trailing Vol from 10/04/2010 to 12/30/2016
ggplot(ZTS, aes(Date, SD)) + ggtitle("ZTS 252-day Trailing Vol") + geom_line() +
xlab("Time") + ylab("252-day rolling SD")

```
